---
title: "iteration_and_listcols"
author: "Xiaoyu Wu"
date: "2023-10-27"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
set.seed(1)
```

## List
You can put anything in the list
```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
mat= matrix(1:8, nrow=2, ncol=4)
# matrix contains number 1 to 8 
summary = summary(rnorm(1000))
```
store everything in the list 
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
# list can have different vectors with different lengths
```

```{r}
l$vec_numeric
l[[1]]
# access individual elements in the list 
l[[1]][1:3]
# access the 1st and 3rd elements in the first vector of the list 
```

## `for` loops
new list 
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )
list_norms
is.list(list_norms)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```
apply simple mean_and_sd function to list_norm 
```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```
Let's use a for loop: 
```{r}
output_mean_and_sd = vector("list", length = 4)
output_median = vector("list", length = 4)
# define two output lists with the same number of entries as my target dataframe
for (i in 1:4) {
  output_mean_and_sd[[i]] = mean_and_sd(list_norms[[i]])
  output_median[[i]] = median(list_norms[[i]])
}
# input is list_norms 
output_mean_and_sd
output_median
```

## Let's try map
```{r}
output = map(list_norms, mean_and_sd)
# The first argument to map is the list we want to iterate over, and the second argument is the function we want to apply to each element.
output = map(.x = list_norms, ~ mean_and_sd(.x))
# be more specific in giving arguments to map
```

## map variants
```{r}
output = map_dbl(list_norms, median, .id = "input")
# Using the .id argument keeps the names of the elements in the input list.
# put the names of each list into a new variable called "input"
```

```{r}
output = map_dfr(list_norms, mean_and_sd, .id = "input")
# this will produce a single data frame.
# map_int or map_lgl, integer or a logical.
```

```{r}
# output = map2(input_1, input_2, \(x,y) func(arg_1 = x, arg_2 = y))
```

## List columns and operations
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```

```{r}
listcol_df %>% pull(name)
```

```{r}
listcol_df %>% pull(samp)
```

```{r}
listcol_df$samp[[1]]
```

```{r}
listcol_df |> 
  filter(name=="a")
```

apply mean_and_sd to the first element of our list column
```{r}
mean_and_sd(listcol_df$samp[[1]])
```

```{r}
map(listcol_df$samp, mean_and_sd)
```
store the results as a new list column
```{r}
listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd))  %>% 
  select(name,summary) %>%
  unnest(summary)
listcol_df
```
## Revisiting NSDUH
```{r}
nsduh_table <- function(html, table_num) {
  
  table = 
    html |> 
    html_table() |> 
    nth(table_num) |>
    slice(-1) |> 
    select(-contains("P Value")) |>
    pivot_longer(
      -State,
      names_to = "age_year", 
      values_to = "percent") |>
    separate(age_year, into = c("age", "year"), sep = "\\(") |>
    mutate(
      year = str_replace(year, "\\)", ""),
      percent = str_replace(percent, "[a-c]$", ""),
      percent = as.numeric(percent)) |>
    filter(!(State %in% c("Total U.S.", "Northeast", "Midwest", "South", "West")))
  
  table
}
```

```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)

output = vector("list", 3)

for (i in c(1, 4, 5)) {
  output[[i]] = nsduh_table(nsduh_html, i)
}

nsduh_results = bind_rows(output)
```

```{r}
nsduh_results = 
  map(c(1, 4, 5), nsduh_table, html = nsduh_html) |> 
# I’m supplying the html argument after the name of the function that I’m iterating over.
  bind_rows()
```

```{r}
nsduh_results= 
  tibble(
    name = c("marj", "cocaine", "heroine"),
    number = c(1, 4, 5)) |> 
  mutate(table = map(number, \(num) nsduh_table(html = nsduh_html, num))) |> 
  unnest(cols = "table")
```

## Nested data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
Weather data will be separated into three station-specific data frames
```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest
```

```{r}
weather_nest %>% pull(name)
```

```{r}
weather_nest %>% pull(data)
```
unnesting 
```{r}
unnest(weather_nest, cols = data)
```
 fit the simple linear regression relating tmax to tmin
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
```
apply our weather_lm function to each data frame using map
```{r}
map(weather_nest$data, weather_lm)
map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
# avoid the creation of a dedicated function
```
using a for loop:
```{r}
output=vector("list",3)

for (i in 1:3) {
  output[[i]]=weather_lm(weather_nest$data[[i]])
}
output
```

mutate to fit this model, and to store the result in the same dataframe
What about a amap in a list column!!!!!??
```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest
```

