---
title: "iteration_and_listcols"
author: "Xiaoyu Wu"
date: "2023-10-27"
output: github_document
---

```{r}
library(tidyverse)

set.seed(1)
```

## List
You can put anything in the list
```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
mat= matrix(1:8, nrow=2, ncol=4)
# matrix contains number 1 to 8 
summary = summary(rnorm(1000))
```
store everything in the list 
```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

```{r}
l$vec_numeric
l[[1]]
# access individual elements in the list 
l[[1]][1:3]
```

## `for` loops
new list 
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )
list_norms
is.list(list_norms)
```

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```
apply simple mean_and_sd function to list_norm 
```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```
Let's use a for loop: 
```{r}
output = vector("list", length = 4)
# define an output list with the same number of entries as my target dataframe
for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
output
```

## Let's try map
```{r}
output = map(list_norms, mean_and_sd)
# The first argument to map is the list we want to iterate over, and the second argument is the function we want to apply to each element.
output = map(.x = list_norms, ~ mean_and_sd(.x))
# be more specific in giving arguments to map
```

## map variants
```{r}
output = map_dbl(list_norms, median, .id = "input")
# Using the .id argument keeps the names of the elements in the input list.
# put the names of each list into a new variable called "input"
```

```{r}
output = map_dfr(list_norms, mean_and_sd, .id = "input")
# this will produce a single data frame.
# map_int or map_lgl, integer or a logical.
```

```{r}
output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y))
# we have two arguments
```

## List columns and operations
```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```

```{r}
listcol_df %>% pull(name)
```

```{r}
listcol_df %>% pull(samp)
```

```{r}
listcol_df$samp[[1]]
```

```{r}
listcol_df |> 
  filter(name=="a")
```

apply mean_and_sd to the first element of our list column
```{r}
mean_and_sd(listcol_df$samp[[1]])
```

```{r}
map(listcol_df$samp, mean_and_sd)
```
store the results as a new list column
```{r}
listcol_df = 
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd))

listcol_df
```
## Nested data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
Weather data will be separated into three station-specific data frames
```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest
```

```{r}
weather_nest %>% pull(name)
```

```{r}
weather_nest %>% pull(data)
```
unnesting 
```{r}
unnest(weather_nest, cols = data)
```
 fit the simple linear regression relating tmax to tmin
```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}
```
apply our weather_lm function to each data frame using map
```{r}
map(weather_nest$data, weather_lm)
map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
# avoid the creation of a dedicated function
```
using a for loop:
```{r}
output=vector("list",3)

for (i in 1:3) {
  output[[i]]=weather_lm(weather_nest$data[[i]])
}
output
```

mutate to fit this model, and to store the result in the same dataframe
What about a amap in a list column!!!!!??
```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest
```

## Revisiting Napoleon
```{r}
read_page_reviews <- function(url) {
  
  html = read_html(urls[1])
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text() %>% 
    magrittr::extract(3*(1:10))
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```
five pages of reviews 
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

```{r}
dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()
```

