---
title: "writing_functions"
author: "Xiaoyu Wu"
date: "2023-10-25"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)

set.seed(1)
```

## Do something simple 
```{r}
x_vec = rnorm(30, mean = 5, sd = 3)
# 30 vectors taking the mean of 5 and sd of 3 
(x_vec - mean(x_vec)) / sd(x_vec)
# z-scores: subtracted by the mean and divided by sd
```
I wanta function to compute z-scores 
```{r}
z_scores = function(x) {
# argument is x and inside the brackets 
# input is x everywhere 
  z = (x - mean(x)) / sd(x)
# body and operation 
  return(z)
# return objects   
}

z_scores(x_vec)
```
Try my functions on some other thing 
```{r}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
# update teh function 
  z = mean(x) / sd(x)
  
  z
}
# add some checks 
```

## Multiple outputs 
store each of the values in a named list
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  list(mean = mean_x, 
       sd = sd_x)
}
mean_and_sd(x_vec)
```
store values in a data frame
```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
mean_and_sd(x_vec)
```

## Multiple inputs
```{r}
sim_data = tibble(
  x = rnorm(30, mean = 2, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```
I'd like to do this in a function 
```{r}
sim_mean_sd = function(sample_size, mu, sigma) {
# true population mean mu and true population sd sigma.
# (sample_size, mu=3, sigma=4) default values 
  sim_data = tibble(
    x = rnorm(n=sample_size, mean = mu, sd = sigma),
  )
# inputs  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
# return objects 
}
sim_mean_sd(sample_size=100,mu=6,sigma=3)
```

## Revisiting past examples
Scraping Amazon
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

html = read_html(url)

review_profile = 
    html %>%
    html_nodes(".a-profile-content") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes(".review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_date = 
    html %>%
    html_nodes(".review-date") %>%
    html_text() 

reviews=
    tibble(
    profile = review_profile,
    stars = review_stars,
    date = review_date
)
reviews
```
Let's turn that code into a function 
```{r}
read_page_reviews = function(url) {
# input is the url 
  html = read_html(url)
  
  review_profile = 
    html %>%
    html_nodes(".a-profile-content") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes(".review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_date = 
    html %>%
    html_nodes(".review-date") %>%
    html_text() 
  
  reviews=
    tibble(
    profile = review_profile,
    stars = review_stars,
    date = review_date
  )
  # body and operations   
  reviews
# return objects 
}

dynamite_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"
read_page_reviews(dynamite_url)
```
read in reviews from a few pages and combine the results
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)
```

## Mean scoping example 
```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
# y is the needed value for x 
```

## Functions as arguments
```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}
mean(x_vec)
median(x_vec)
my_summary(x_vec, mean)
# reorder summ_func according to the mean 
```
